Binary companions of red clump stars

### 2017-07-29 paper/main.tex
description lists

Now we want to take the individual-star fits---or samplings---that
we made in \sectionname~\ref{sec:fitting} and, from these, produce
an inference of the properties of the whole \RC\ binary-star population.
Important necessary properties of this inference are the following:
\begin{description}
\item[foo] whatevs
\item[bar] and other
\end{description}
We can meet these requirements with a hierarchical Bayesian inference
(hierarchical probablistic model) of the binary-star population.

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[foo] whatevs
\item[bar] and other
\end{description}

>>>>

Now we want to take the individual-star fits---or samplings---that
we made in \sectionname~\ref{sec:fitting} and, from these, produce
an inference of the properties of the whole \RC\ binary-star population.
Important necessary properties of this inference are the following:
\begin{description}
\item[utilize non-detections] Even stars which are consistent with
  zero radial-velocity variation (no binary companion) are relevant to
  a populations inference. This is for two reasons: The first is that
  the small-mass and long-period ends of the binary population will
  imprint only low-amplitude signals in the data. These signals are
  present at low signal-to-noise, but not if we remove them because
  they don't make some catalog or threshold cut. The second reason
  these stars are important is that they constrain the fraction of
  stars with no companions. Any populations-inference method we employ
  must responsibly harvest the information in these non-detection
  stars.
\item[marginalize out individual-star parameters] Every star---even
  any star with a high-confidence companion detection---will have a
  highly multi-modal likelihood function, with many qualitatively
  different companion models that are nonetheless locally
  optimal. This means that most posterior samplings (created in
  \sectionname~\ref{sec:fitting}) under our interim prior will show
  multiple, qualitatively distinct modes in binary-system parameter
  space.  Any correct population inference will marginalize out these
  extremely non-trivial distributions over individual-star
  binary-system parameters.
\end{description}
We can meet these requirements---at least in principle---with a
hierarchical Bayesian inference (hierarchical probablistic model) of
the binary-star population.

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[population parameterization] whatevs
\end{description}
